---
title: "FCMP functions/subroutines in 'aux' group"
output:
rmdformats::readthedown:
lightbox: true
use_bookdown: true
---
 
```{r setup, echo =FALSE}
sasprog_nm <- "_auxiliary"   # Matches this SAS prog name
vgr_nm <- "aux"
library(rmdformats)
# https://www.r-bloggers.com/2019/09/create-rmarkdown-document-with-sas-code-and-output-sas-engine/
saspath <- "C:/Program Files/SASHome/SASFoundation/9.4/sas.exe"
```
 
#  "{r vgrp_nm}" FCMP group {#aux-anchor};
 
This section includes information on FCMP functions/subroutines from "aux" group
xyz
xyz
 
```{r , echo=FALSE}
fun_nm <- "FQ_fun"
```
 
##  Function `FQ_fun` {#aux-FQ_fun-anchor};
 
<!---  FQ_fun function description --->
`FQ_fun` is an auxiliary function in "aux" FCMP group.
 
_Purpose:_ Recoding variable
 
_Arguments:_
 
* `studyr`: Redundant argument
* `var_old`: Variable to be recoded
 
_Syntax:_
 
```{r, eval=FALSE}
new_var = FQ_fun(1992, var_old);
```
 
xyz
xyz/* FQ_fun source starts here */
xyz
xyzfunction FQ_fun(studyyr, var_old) group ="aux";
xyz
xyz/* Auxiliary function */
xyzvar_new = var_old;
xyz
xyzselect (var_old);
xyzwhen (1) var_new = 1;
xyzwhen (5) var_new = 0;
xyzwhen (97) var_new =.O;
xyzwhen (.,-8) var_new =.M;
xyzwhen (8,98) var_new =.D;
xyzwhen (9,99) var_new =.R;
xyzotherwise;
xyzend;
xyzreturn(var_new);
xyzendsub; /* end function FQ_fun */
xyz*END*;
xyz
xyz
xyz
xyz/* Insert SAS Example here */
xyzdata dt;
xyzx=33;
xyzrun;
xyzproc print data;
xyzrun;
xyz*END*;
xyz
xyz
Output: `FQ_fun` function (aux group);
 
```{sas, ref.label = "FQ_fun-example", echo= FALSE, eval = TRUE, engine.path = saspath};
```;
xyz
xyz
 
```{r , echo=FALSE}
fun_nm <- "studyyr_ok"
```
 
 
xyz
xyz
xyzfunction studyyr_ok(yr) group ="aux";
xyzok  = 1;
xyzselect;
xyzwhen(yr = .)    ok =0;
xyzwhen(yr < 1992) ok =0;
xyzwhen(yr > 1996 and mod(yr,2)=1) ok =0;
xyzwhen(yr > 2030) ok = 0;
xyzotherwise;
xyzend;
xyzreturn(ok); /* function studyyr_ok */
xyzendsub;
xyz
xyzfunction data_exist(ref $) group = "aux";
xyzrc = exist(ref);
xyzif (ref = "") then rc=0;
xyzreturn(rc);
xyzendsub;
xyz
