/*+RMD Note: General info on _auxiliary.sas STARTS
---
title: "FCMP functions/subroutines in 'aux' group"
output:
rmdformats::readthedown:
lightbox: true
use_bookdown: true
---
 
```{r setup, echo =FALSE}
sasprog_nm <- "_auxiliary"   # Matches this SAS prog name
vgr_nm <- "aux"
library(rmdformats)
# https://www.r-bloggers.com/2019/09/create-rmarkdown-document-with-sas-code-and-output-sas-engine/
saspath <- "C:/Program Files/SASHome/SASFoundation/9.4/sas.exe"
```
 
 
#  "{r vgrp_nm}" FCMP group {#aux-anchor};
 
This section includes information on FCMP functions/subroutines from "aux" group
-*/  * General info on _auxiliary.sas ENDS here;
 
 
/*+RMD NOTE: ---> FQ_fun description starts here
 
```{r , echo=FALSE}
fun_nm <- "FQ_fun"
```
 
##  Function `FQ_fun` {#aux-FQ_fun-anchor};
 
<!---  FQ_fun function description --->
`FQ_fun` is an auxiliary function in "aux" FCMP group.
 
_Purpose:_ Recoding variable
 
_Arguments:_
 
* `studyr`: Redundant argument
* `var_old`: Variable to be recoded
 
_Syntax:_
 
```{r, eval=FALSE}
new_var = FQ_fun(1992, var_old);
```
 
-*/  * Note: General info on _auxiliary.sas ENDS */
 
/* FQ_fun source starts here (note lines starting with <*+RMD > and <*- >comment */
 
*+ {r FQ_fun-src, eval = FALSE};
function FQ_fun(studyyr, var_old) group ="aux";
 
/* Auxiliary function */
var_new = var_old;
 
select (var_old);
when (1) var_new = 1;
when (5) var_new = 0;
when (97) var_new =.O;
when (.,-8) var_new =.M;
when (8,98) var_new =.D;
when (9,99) var_new =.R;
otherwise;
end;
return(var_new);
endsub; /* end function FQ_fun */
```
 
/* FQ_fun example starts here */
 
_Example_;
 
*+ {r FQ_fun-example, eval =FALSE};
/* Insert SAS Example here */
;
 
Output: `FQ_fun` function (aux group);
*+ {sas, ref.label = "FQ_fun-example", echo= FALSE, eval = TRUE, engine.path = saspath};
;
 
/*+RMD NOTE: ---> `studyyr_ok` function description starts here
 
```{r , echo=FALSE}
fun_nm <- "FQ_fun"
```
 
 
* NOTE: ---> `studyyr_ok` function description ends here;
 
 
ction studyyr_ok(yr) group ="aux";
= 1;
ect;
n(yr = .)    ok =0;
n(yr < 1992) ok =0;
n(yr > 1996 and mod(yr,2)=1) ok =0;
n(yr > 2030) ok = 0;
erwise;
;
urn(ok); /* function studyyr_ok */
sub;
 
ction data_exist(ref $) group = "aux";
= exist(ref);
(ref = "") then rc=0;
urn(rc);
sub;
 
