---
title: "ADL/IADL FCMP functions/subroutines"
output:
  rmdformats::readthedown:
     lightbox: true
     use_bookdown: true
---


# ***ADL/IADL domain***  

This section contains ADL/IADL FCMP functions/subroutines organized in various groups.



```{r sas-ininit, echo= FALSE}
 library(rmdformats)

 # https://www.r-bloggers.com/2019/09/create-rmarkdown-document-with-sas-code-and-output-sas-engine/
 saspath <- "C:/Program Files/SASHome/SASFoundation/9.4/sas.exe"
```


```{r, echo =FALSE}
# Tracing execution
Tinit <-  "ADL-main-"
Tr <-  paste0(Tinit,1)
```

<!--- ================= FCMP GROUP STARTS HERE =========================== --->
<!--- =====               aux group starts                            ==== --->

#  "aux" FCMP group {#aux-anchor}
 

This section includes information on FCMP functions/subroutines from "aux" group


## `FQ_fun` function 

```{r child-ADL-aux, child = 'sections/ADL-aux-FQ_fun.Rmd'}
```

```{r, echo =FALSE}
# Tracing execution
T1 <-  paste0(Tinit, 500)
```


<!--- ================= FCMP GROUP STARTS HERE =========================== --->
<!--- ===== binder FCMP group ==== --->

#  "binder" FCMP group {#binder-anchor}

This section includes information on FCMP functions/subroutines from "binder" group.

## `dispatch_datain` function 

```{r child-ADL-aux, child = 'sections/ADL-binder-dispatch_datain.Rmd'}
```


```{r, echo =FALSE}
# Tracing execution
T1 <-  paste0(Tinit,1)
```

